Response Patterns

### 2024-12-17 manuscript/manuscript.qmd
some minor updates

---
title: "Planning to Save Energy: How Information Format Affects Accuracy"
aliases:
  - /manuscript.html
format:
    wordcount-html: 
        #output-file: index.html
        wordcount-banner: true
        theme: 
            - zephyr
            - ../assets/custom.scss
        toc: true
        shift-heading-level-by: 1
        title-block-banner: "#000D51"
        include-in-header:
            - text: |
                <style type="text/css">
                h2.hide {
                    display: none;
                }
                </style>
    html: 
      echo: true
      code-fold: show
      output-file: manuscript-code.html
    hugo-md:
        include: false
        echo: false
        html-math-method: mathjax
        output-file: manuscript_hugo.md
        suppress-bibliography: true
    gfm:
        echo: true
        output-file: manuscript_gfm.md
        suppress-bibliography: true
    hikmah-manuscript-pdf:
        output-file: rep_study.pdf
        mainfont: "Linux Libertine O"
        mainfontoptions:
        - "Numbers=Proportional"
        - "Numbers=OldStyle"
        mathfont: "Libertinus Math"
        knitr:
            opts_chunk:
                dev: "cairo_pdf"
    #hikmah-manuscript-docx: default
    docx: default
format-links:   
    - text: HTML
      href: manuscript.html
      icon: file-minus
    - text: HTML (with code)
      href: manuscript-code.html
      icon: file-plus
    - format: hikmah-manuscript-pdf
      text: PDF version
      icon: file-pdf
    - docx
    - gfm
date: 2024-12-07
abstract: |
    This study aims to examine how the format of energy information impacts individuals’ ability to develop precise energy reduction plans. By manipulating the reference class (kWh, %, USD) and assessing planning accuracy, we seek to determine which format facilitates better comprehension and decision-making.Across two experiments, the kWh format generally led to better accuracy, while the USD format consistently led to the worst performance. These findings highlight the importance of effective information presentation to promote energy conservation, and may contribute to the development of more effective energy communication strategies that can enhance conservation efforts.
---

@@

Energy poverty continues to be a pervasive issue in the United States @memmottSociodemographicDisparitiesEnergy2021. This challenge partly arises from difficulties in converting information across numerical formats, impeding the development of precise energy reduction plans @reimerNumericCommunicationRisk2015. Prior research by @canfieldPerceptionsElectricityuseCommunications2017 demonstrated that presenting energy information in tabular formats enhances comprehension relative to graphs.

The way numerical information is presented can significantly affect how individuals process and use that information [@reimerNumericCommunicationRisk2015] . The reference class problem highlights that numbers without clear reference points can lead to misinterpretation, as the meaning of a statistic depends on the category or class it refers to [@gigerenzerSimpleToolsUnderstanding2003; @reimerNumericCommunicationRisk2015]. Presenting energy information in absolute units (e.g., kWh) provides a clear reference class, potentially enhancing comprehension.

@@

@tbl-s1-agg that participants in the kWh condition met the target goal 38% of the time, compared to 22% for the Percentage condition and 10% for the USD condition. Moreover, the kWh reference class exhibited smaller deviations from the target reduction, suggesting that participants performed more accurately when the goal was framed in kWh rather than percentages or USD.

@@

Experiment 1 examined how different numerical representations of energy reduction goals influenced participants’ planning accuracy. In line with our hypothesis that absolute units would yield better accuracy, the kWh condition supported significantly more precise energy reduction plans than did either the Percentage or USD conditions. Although the Percentage format was detrimental to accuracy relative to kWh, it was the USD condition that consistently produced the poorest outcomes, suggesting that monetary terms, while intuitive in everyday contexts, may not serve as effective reference classes for planning appliance-specific reductions in energy use.

@@

The experimental procedures in study 2 are quite similar to those in study 1, but we also included a rounding manipulation (rounded vs. not rounded), and a manipulation of the goal (10% reduction vs. 15% rediction). We recruited 206 participants from Amazon Mechanical Turk, but data from from 10 participants were corrupted due to experimenter error, leaving a final sample of 196 participants.

Note that reference class remains a between-subjects variable, while percent goal, rounding, and state are within-subjects variables. In study 2, the new design is a 4 state temperature (2 warm vs. 2 cold states) X 2 task goal (10% vs. 15%) X 2 last year’s usage for the family and the state average (exact vs. rounded numbers) within X 3 task reference class (USD vs. Percentage vs. kWh) between.

@@

As in Experiment 1, we further investigated the role of individual differences in energy literacy in predicting planning accuracy. A Bayesian linear regression model, analogous to the one used in Experiment 1 (log_abs_error ~ els + (1|id) + (1|state)), revealed a significant negative relationship between energy literacy scores and log-transformed absolute error (Estimate = -3.21, 95% CI: -3.89 to -2.52). This finding indicates that participants with higher energy literacy tended to produce more accurate plans, exhibiting smaller deviations from the target reduction goals. The conditional effect plot (@fig-s2-els) visually confirms this relationship, showing a clear decreasing trend in log absolute error as energy literacy increases.

@@

@@

@@

>>>>

---
title: "Planning to Save Energy: How Information Format Affects Accuracy"
aliases:
  - /manuscript.html
format:
    wordcount-html: 
        #output-file: index.html
        wordcount-banner: true
        theme: 
            - zephyr
            - ../assets/custom.scss
        toc: true
        shift-heading-level-by: 1
        title-block-banner: "#000D51"
        include-in-header:
            - text: |
                <style type="text/css">
                h2.hide {
                    display: none;
                }
                </style>
    html: 
      echo: true
      code-fold: show
      output-file: manuscript-code.html
    hugo-md:
        include: false
        echo: false
        html-math-method: mathjax
        output-file: manuscript_hugo.md
        suppress-bibliography: true
    gfm:
        echo: true
        output-file: manuscript_gfm.md
        suppress-bibliography: true
    hikmah-manuscript-pdf:
        output-file: rep_study.pdf
        mainfont: "Linux Libertine O"
        mainfontoptions:
        - "Numbers=Proportional"
        - "Numbers=OldStyle"
        mathfont: "Libertinus Math"
        knitr:
            opts_chunk:
                dev: "cairo_pdf"
    #hikmah-manuscript-docx: default
    docx: default
format-links:   
    - text: HTML
      href: manuscript.html
      icon: file-minus
    - text: HTML (with code)
      href: manuscript-code.html
      icon: file-plus
    - format: hikmah-manuscript-pdf
      text: PDF version
      icon: file-pdf
    - docx
    - gfm
date: 2024-12-07
abstract: |
    Effective communication of energy consumption information is crucial for promoting residential energy conservation. This study investigates how different numerical representations of energy reduction goals influence consumers' ability to create accurate conservation plans. Across two experiments, we examined the impact of presenting energy information in kilowatt-hours (kWh), percentages, or U.S. dollars (USD) on planning accuracy. Participants completed a simulated household planning task in which they allocated energy usage across multiple appliances, with the goal presented in either kilowatt-hours (kWh), percentages, or monetary costs. Results across both experiments showed that presenting reduction goals in absolute units (kWh) led to significantly greater accuracy compared to percentage-based or monetary formats. Furthermore, we found that higher energy literacy was associated with more accurate planning. These findings demonstrate that absolute units (kWh) are more effective for communicating energy-saving goals, and highlight the potential value of educational interventions to improve consumer energy literacy.
---

@@

Energy poverty continues to be a pervasive issue in the United States [@memmottSociodemographicDisparitiesEnergy2021]. This challenge partly arises from difficulties in converting information across numerical formats, impeding the development of precise energy reduction plans @reimerNumericCommunicationRisk2015. Prior research by @canfieldPerceptionsElectricityuseCommunications2017 demonstrated that presenting energy information in tabular formats enhances comprehension relative to graphs.

The way numerical information is presented can significantly affect how individuals process and use that information [@reimerNumericCommunicationRisk2015]. The reference class problem highlights that numbers without clear reference points can lead to misinterpretation, as the meaning of a statistic depends on the category or class it refers to [@gigerenzerSimpleToolsUnderstanding2003; @reimerNumericCommunicationRisk2015]. Presenting energy information in absolute units (e.g., kWh) provides a clear reference class, potentially enhancing comprehension.

@@

@tbl-s1-agg that participants in the kWh condition met the target goal 38% of the time, compared to 22% for the Percentage condition and 10% for the USD condition. Moreover, the kWh reference class exhibited smaller deviations from the target reduction, suggesting that participants performed more accurately when the goal was framed in kWh rather than when percentages or USD.

@@

Experiment 1 examined how different numerical representations of energy reduction goals affected participants’ planning accuracy. In line with our hypothesis that absolute units would yield better accuracy, the kWh condition supported significantly more precise energy reduction plans than did either the Percentage or USD conditions. Although the Percentage format was detrimental to accuracy relative to kWh, it was the USD condition that consistently produced the poorest outcomes, suggesting that monetary terms, while intuitive in everyday contexts, may not serve as effective reference classes for planning appliance-specific reductions in energy use.

@@

The experimental procedures in Experiment 2 are quite similar to those in Experiment 1. Experiment 2 employed a 2 (task goal: 10% vs. 15% reduction) x 2 (last year's usage: exact vs. rounded) within-subjects design, with a between-subjects manipulation of the reference class (USD vs. Percentage vs. kWh).. We recruited 206 participants from Amazon Mechanical Turk, but data from from 10 participants were corrupted due to experimenter error, leaving a final sample of 196 participants.

@@

As in Experiment 1, we further investigated the role of individual differences in energy literacy in predicting planning accuracy. A Bayesian linear regression model, analogous to the one used in Experiment 1 (log_abs_error ~ els + (1|id) + (1|state)), revealed a significant negative relationship between energy literacy scores and log-transformed absolute error (Estimate = -3.21, 95% CI: -3.89 to -2.52). This finding indicates that participants with higher energy literacy scores tended to produce more accurate plans, exhibiting smaller deviations from the target reduction goals. The conditional effect plot (@fig-s2-els) visually confirms this relationship, showing a clear decreasing trend in log absolute error as energy literacy increases.

@@

Experiment 2 expanded on the findings of Experiment 1 by introducing additional manipulations of goal difficulty (10% vs. 15% reduction) and numerical presentation (rounded vs. exact numbers). The results largely corroborated and extended those of Experiment 1, providing further evidence for the advantages of presenting energy reduction goals in absolute units (kWh).

@@

Across two experiments, we consistently found that presenting energy reduction goals in absolute units (kWh) led to more accurate planning compared to percentage-based or monetary representations. This advantage persisted across variations in goal difficulty and numerical presentation, suggesting a robust effect of reference class on planning accuracy.

@@

Mention @blaschBoundedlyRationalConsumers2019 - better long-term appliance selection with information presented in monetary terms.

### 2024-12-17 manuscript/test.qmd
some minor updates

@@

- @canfieldPerceptionsElectricityuseCommunications2017 found that tables were more effective than graphs for conveying specific electricity usage data, likely because tables facilitate straightforward point reading. However, they also noted that individuals with lower energy literacy had reduced comprehension across all formats.
- @canfieldPerceptionsElectricityuseCommunications2017's findings on preferences for historical use information and the impact of neighbor comparisons
- The concept of cognitive fit posits that performance improves when the information presentation format aligns with the task requirements [@vesseyCognitiveFitTheoryBased1991]
- alignment can reduce cognitive load and enhance accuracy in planning [@shahBarLineGraph2011]
- Reimer et al. (2015) provide  context on how numerical formats affect risk perception, the reference class problem, and the benefits of natural frequencies.

@@

>>>>

This study aims to examine how the format of energy information impacts individuals’ ability to develop precise energy reduction plans. By manipulating the reference class (kWh, %, USD) and assessing planning accuracy, we seek to determine which format facilitates better comprehension and decision-making.Across two experiments, the kWh format generally led to better accuracy, while the USD format consistently led to the worst performance. These findings highlight the importance of effective information presentation to promote energy conservation, and may contribute to the development of more effective energy communication strategies that can enhance conservation efforts.

@@

- @canfieldPerceptionsElectricityuseCommunications2017 found that tables were more effective than graphs for conveying specific electricity usage data, likely because tables facilitate straightforward point reading. However, they also noted that individuals with lower energy literacy had reduced comprehension across all formats.
- @canfieldPerceptionsElectricityuseCommunications2017's findings on preferences for historical use information and the impact of neighbor comparisons

- alignment can reduce cognitive load and enhance accuracy in planning [@shahBarLineGraph2011]
- Reimer et al. (2015) provide  context on how numerical formats affect risk perception, the reference class problem, and the benefits of natural frequencies.

@@

@abrahamseReviewInterventionStudies2005

@attariEnablingEnergyConservation2015

@dewatersEnergyLiteracySecondary2011

@gigerenzerSimpleToolsUnderstanding2003

@larrickMPGIllusion2008

@blaschBoundedlyRationalConsumers2019

@fischerFeedbackHouseholdElectricity2008

@schwartzWhatPeopleConsumption2015

@vongrabeUsingInstanceBasedLearning2020

@gigerenzerHowImproveBayesian1995

@attariPublicPerceptionsEnergy2010

@herrmannDoesDataVisualization2018

@vandenbroekHeuristicsEnergyJudgement2019

@herberzKiloWhatDefault2020

@marghetisSimpleInterventionsCan2019

@lagomarsinoNeedChargeRight2022

@hahnelMentalAccountingMechanisms2020

@delgadoOpportunitiesGreaterEnergy2018

@schleyCognitiveAccessibilityJudgments2015

@langeWorkEnvironmentalProtection2021

@tiedeNumeracyNumericAttention2022

### 2024-12-17 misc/indiv.qmd
some minor updates

>>>>

# Model the relationship between calculator use, reference class, and absolute error
model_calc <- lm(log_abs_error ~ calc * refClass, data = s2_long)
summary(model_calc)

# Visualize the relationship
ggplot(s2_long, aes(x = refClass, y = log(abs_error), fill = calc)) +
  geom_boxplot() +
  labs(title = "Planning Accuracy by Calculator Use and Reference Class")
